Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-07 arxiv/proof_examples.tex
revise

		 g(x) \define & \left\| X^{(1)} \Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
		& \left. + x X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
		 + & \left\| X^{(2)} \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
		 &\left. + x X^{(2)}\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 

@@

	where we denote {\cor revise}
	$$ \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
\HZ{could you align the Eq so that they look better on page?}

@@

&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
= &\left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \\
&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \\
& +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
		&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
&+ 2 A^2 \sigma^2 \tr\left[ \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
		& = \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).

@@

&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \nonumber\\
&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}

@@

where in the first step we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
 & (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} + A^2   (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)}  \\
 &=  (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} + A^2  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}  \\
 & =   (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} .
Here in the first step of the above derivation, we used that 
 $$(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)}.$$

Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation. %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
 \begin{claim}\label{claim_largedev1}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
for any small constant $c>0$.
	 \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
 \end{claim}
 \begin{proof}
By Fact \ref{lem_minv} (iii), we have that with high probability,
 \be\label{op_X12}
\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
 \ee
 and
 \be\label{op_Sig1}
\| \Sigma(A)^{-1}\|\le \frac1{A^2((\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}})+((\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}) }\lesssim \frac{1}{(A^2+1)p},
 \ee
 where we also used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$ for a small constant $\tau>0$.

 Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
 \begin{align}
 & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
 &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,\label{expand_6}
 \end{align}
 where
 \begin{align*}
&h_1(A):=  (\beta_1-A\beta_2)^\top (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)  ,\\
& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
& h_3(A):=  A^2 { (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
& h_4(A):=  (\epsilon^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1), \\
&h_5(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1),\\
&h_6(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
\end{align*}
Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.

For $h_1(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $\e_1>0$:
\begin{align}
&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right|\nonumber \\
&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2).\label{eq_hA1}
\end{align}
 Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
\begin{align*}
&\left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \\
&\le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \Sigma(A)^{-1} \right\|^2 \lesssim \frac{p}{(A^2+1)^2}.
\end{align*}  
Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
\be\label{eq_hA23}\left|h_2(A) - \exarg{\epsilon^{(1)}}{h_2(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2, \quad \left|h_3(A) - \exarg{\epsilon^{(2)}}{h_3(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2.\ee
For $h_4(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $\e_1>0$:
\begin{align}
\left|h_4(A)\right| &\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]}\cdot \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
&\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{e_1}\cdot \sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2} \cdot \left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\cdot  \left\|X^{(1)}\right\| \left\|\Sigma(A)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{1/2+e_1}\frac{\sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2}}{A^2+1} \lesssim p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
\end{align}
where in the fourth step we used $\left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality. With same argument, we can show that 
\be\label{eq_hA56} \left|h_5(A)\right| \le p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(A)\right| \le p^{1/2+e_1}\sigma^2,\ee
with high probability for any small constant $e_1>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that

@@

First it is easy to observe that $h(A)< h(-A)$ for $A> 0$. 

>>>>

		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 

@@

	where we denote $ \hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$ We can calculate the partial expectation of $g(x)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
%\HZ{could you align the Eq so that they look better on page?}
&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \nonumber\\
&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2  \nonumber\\
& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \nonumber\\
&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
Using the following identity

@@

(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
we can simplify that 
&  \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
&=(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
&+(\beta_1-x\beta_2)^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\\
%&=(\beta_1-x\beta_2)^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\\
&=(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).
Using this identity and taking expectation over $\epsilon^{(1)}$ and $\epsilon^{(2)}$, we can simplify \eqref{Eg(x)}  to 
		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \\
		&= (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
		& = (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).

@@

&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2} \nonumber\\
%&=[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
%&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}

@@

where we used that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$. 
%and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
% & (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} + A^2   (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}  \\
% &=  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} + A^2  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}  \\
% & =   (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} .

Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(x)$ and its partial expectation. %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
 \begin{claim}\label{claim_largedev1}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
for any small constant $c>0$.
	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
 \end{claim}
 \begin{proof}
By Fact \ref{lem_minv} (iii), we have that with high probability,
 \be\label{op_X12}
\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
 \ee
 and
 \be\label{op_Sig1}
\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
 \ee
where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.

 Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
 \begin{align}
 & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
 \end{align}
 where
 \begin{align*}
&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
\end{align*}
Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.

For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
\begin{align}
&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
\end{align}
 Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
\begin{align*}
 \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\ 
 & \lesssim \frac{p}{(x^2+1)^2}.
\end{align*}  
Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
\begin{align}
&\left|h_4(x)\right| \nonumber\\
&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
\end{align}
where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality. With same argument, we can show that 
\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that

@@

First it is easy to observe that $h(x)< h(-A)$ for $A> 0$. 
